### 2021-09-30 doc/thesis/front/abstract.tex
Incorporate feedback (#32)

The main topic of this thesis is the development of a system design for an embedded system, which combines all the knowledge of different disciplines and topics, that are accumulated over the course of the entire university program.
A system-level design approach is taken to develop an FM radio receiver in multiple implementation variants, targeting a system-on-chip hardware, including an FPGA and a CPU.\\

>>>>

The objective of this thesis is the development of a system design for an embedded system.
A system-level design approach is taken to develop an FM radio receiver in multiple implementation variants, targeting a system-on-chip hardware, including an FPGA and a CPU.\\
